Essays in Computational Management Science

### 2018-05-10 Chapters/Chapter01.tex

\section{Load changing}

@@

\begin{figure}[!htb]
\centering
\subfloat[Only low load scenarios]{\includegraphics[width=\textwidth]{./images01/new2/tips_aggregate2.png}}

\subfloat[All load scenarios]{\includegraphics[width=\textwidth]{./images01/new2/tips_aggregate.png}}

@@

\section{Transaction's classification}

Afterward, to a better visualization of a Hathor's network, I run a simulation classifying the transactions in either confirmed, in-progress, or unconfirmed (tips). I also showed the transactions solving the proof-of-work which had not been propagated yet. See Figure \ref{fig:hathor-dag-big} and notice the chain of blocks inside the DAG.

>>>>

\clearpage

\clearpage

\section{Visualizing the network}

Visualizing the network is not simple because the number of transactions and blocks is high, thus, arranging them and their edges is a non-trivial task. Therefore, most of the visualization are just part of the DAG which shows a window of time.

To a better visualization of a Hathor's network, I run a simulation classifying the transactions in either confirmed, in-progress, or unconfirmed (tips). I also showed the transactions solving the proof-of-work which had not been propagated yet. See Figure \ref{fig:hathor-dag-big} and notice the chain of blocks inside the DAG. Confirmed transactions are in green circles, while in-progress transactions are in white circles and tips are in yellow circles. The blocks are in red boxes form a chain inside the DAG. Finally, the new transactions which are solving the proof-of-work and had not been propagated are in grey dashed circles.

As new transactions have to chose two previous transactions to confirm, and just after they start to work in the proof-of-work, two new transactions eventually may chose the same tip because they do not know each other yet. So, if new transactions are coming in a low pace, the width of the swarm is small because the number of new transactions simultaneously solving the proof-of-work is also small. But, when new transactions are coming in a high volume, the width of the swarm increases because new transactions are choosing the same tip over and over.

In summary, the width of the swarm depends on the number of transactions per second. The greater the number of new transactions per second, the larger the width of the swarm.

To visualize the change in the width of the swarm, I run a simulation with a constant number of transactions per second, which was increased only in a specific window of time. The result can be seen in Figure \ref{fig:hathor-load-changing}, where the number of transactions per second suddenly increases, and the width increases until it reaches a stable value. Then, the number of transactions per second decreases, and the width returns to the previous value.

@@

The number of tips at a given time also depends on the number of new transactions per second. The relationship between them was empirically measured in several simulations with different $\lambda_\text{TX}$.

Analyzing Figure \ref{fig:hathor-tips}, it is easy to notice that both the average and the standard deviation of the number of tips increase when $\lambda_\text{TX}$ increases. According to \citet{tangle2016}, the average has the following equation:

$$\frac{\lambda_\text{TX}}{\log(2)} \frac{2^{w_\text{TX}}}{H}$$

In our simulation, $H = 100,000$ and $w_\text{TX} = 17$, so, the average number of tips should be equal to $1.89 \cdot \lambda_\text{TX}$. This model works best for low values of $\lambda_\text{TX}$, but diverges a little for higher values. For instance, if $\lambda_\text{TX} = 32$, the equation predicts $60.48$ tips on average yet we can check that the average is around $55$ tips.

When $\lambda_\text{TX} \Rightarrow 0$, the number of tips goes towards one. The explanation is that there will be only one new transaction solving the proof-of-work per turn. So, new transactions will always confirm two tips, reducing the number of tips by one---each transaction confirms two tips and create one new one, hence the balance is -1. As it is impossible to have less to have less than one tip, it converges to one.

When the number of tips is one, new transactions must chose a tip and another in-progress transaction. It should only happen in very low load scenarios, like during the launch of the network itself.

\begin{figure}[!htb]
\centering
\subfloat[All load scenarios]{\includegraphics[width=\textwidth]{./images01/new2/tips_aggregate.png}}

\subfloat[Zoom in the left side of (a)]{\includegraphics[width=\textwidth]{./images01/new2/tips_aggregate2.png}}

@@

### 2018-05-10 Chapters/hathor-architecture.tex

Let's assume that the number of transactions per second is constant and does not change over time. Thus, at the beginning, there will be no tips, and the number will increase until it converges to its stable quantity. The process is in transient state until it reaches the stability. Then, it reaches the steady state. Notice that the number of tips also change in steady state, but its average does not change. It just floats around the average.

@@

In order to estimate the number of tips in the steady state, let's consider the process in which the rate of inward tips is $\lambda_\text{TX}$, while the rate of outward tips is $\rho$. Let $K$ be the number of tips at a given time. Thus, after $\Delta t$ seconds, $\Delta \text{tips} = \lambda_\text{TX} \Delta t - \rho K \Delta t$. In the steady state, $\Delta \text{tips} = 0$, hence $K = \frac{\lambda_\text{TX}}{\rho}$.

Finally, the rate of outward tips is twice the rate in which devices solve the proof-of-work of transactions. Let $H$ be the devices' hash rate, then, $\rho = 2 \cdot H \cdot 2^{-w_\text{TX}}$.
%Twice?! It is a number between 1 and 2, but none of them.

Therefore, in the steady state,

$$K = \frac{\lambda_\text{TX} \cdot 2^{w_\text{TX}}}{2H}$$

%$$\frac{\lambda_\text{TX} \cdot 2^{w_\text{TX}}}{2H} \le K \le \frac{\lambda_\text{TX} \cdot 2^{w_\text{TX}}}{H}$$
For further information about the stochastic process of the total number of tips, see \citet{tangle2016}.

>>>>

Let's assume that the number of transactions per second is constant and does not change over time. Thus, at the beginning, there will be no tips, and the number will increase until it converges to its stable quantity. The process is in transient state until it reaches stability. Then, it is in the steady state. Notice that the number of tips also change in steady state, but its average does not. It just floats around the average.

@@

\citet{tangle2016} has modeled the stochatic process of the total number of tips. It proves that the average number of tips, in the steady state, is:

$$\frac{\lambda_\text{TX} \cdot 2^{w_\text{TX}}}{\log(2)H}$$

%$$\frac{\lambda_\text{TX} \cdot 2^{w_\text{TX}}}{2H} \le K \le \frac{\lambda_\text{TX} \cdot 2^{w_\text{TX}}}{H}$$
